---
title: "example-data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example-data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Example metricminer data

```{r}
library("metricminer")
```

## Calendly Data Examples

[Read more about the calendly API docs here](https://developer.calendly.com/api-docs).

### User

`get_calendly_user()` returns this type of data.

```{r}
get_example_data("calendly_user")
class(calendly_user)
str(calendly_user)
```

### Events

`list_calendly_events()` returns this type of data.

```{r}
get_example_data("calendly_events")
class(calendly_events)
str(calendly_events)
```

## GitHub Data Examples

[Read more about the GitHub API here](https://docs.github.com/en/rest).

### Github user

`get_github_user()` returns this type of data.

```{r}
get_example_data("gh_user")
class(gh_user)
str(gh_user)
```

### Github repository list

`get_user_repo_list()` returns this type of data.

```{r}
get_example_data("gh_repo_list")
class(gh_repo_list)
str(gh_repo_list)
```

### GitHub repository metrics

`get_github_repo_summary()` returns this kind of data.

```{r}
get_example_data("gh_repo_summary_metrics")
class(gh_repo_summary_metrics)
str(gh_repo_summary_metrics)
```

`get_github_repo_timecourse()` returns this kind of data.

```{r}
get_example_data("gh_repo_timecourse_metrics")
class(gh_repo_timecourse_metrics)
str(gh_repo_timecourse_metrics)
```

### Multiple GitHub repositories metrics

`get_multiple_repos_metrics()` returns this kind of data.

```{r}
get_example_data("gh_repos_metrics")
class(gh_repos_metrics)
str(gh_repos_metrics)
```

## Google Analytics Examples

[Read more about the Google Analytics API here](https://developers.google.com/analytics/devguides/reporting/data/v1).

### GA user info

`get_ga_user()` returns this kind of data.

```{r}
get_example_data("ga_user")
class(ga_user)
str(ga_user)
```

### GA properties

`get_ga_properties()` returns this kind of data.

```{r}
get_example_data("ga_properties")
class(ga_properties)
str(ga_properties)
```

### GA property metadata

`get_ga_metadata()` returns this kind of data.

```{r}
get_example_data("ga_property_metadata")
class(ga_property_metadata)
str(ga_property_metadata)
```

### GA property metrics

`get_ga_stats()` when `stats_type = "metrics"` returns this kind of data.

```{r}
get_example_data("ga_metrics")
class(ga_metrics)
str(ga_metrics)
```

### GA property dimensions

`get_ga_stats()` when `stats_type = "dimensions"` returns this kind of data.

```{r}
get_example_data("ga_dimensions")
class(ga_dimensions)
str(ga_dimensions)
```

### GA property link clicks

`get_ga_stats()` when `stats_type = "link_clicks"` returns this kind of data.

```{r}
get_example_data("ga_link_clicks")
class(ga_link_clicks)
str(ga_link_clicks)
```

### Bulk retrieval of GA property metrics/dims/link clicks

`get_all_ga_metrics()` returns this kind of data.

```{r}
get_example_data("ga_all_metrics")
class(ga_all_metrics )
str(ga_all_metrics)
```

## Google Form Examples

[Read more about the Google Form API here](https://developers.google.com/forms/api/reference/rest).

### Single google form

`get_google_form()` returns this kind of data.

```{r}
get_example_data("gform_info")
class(gform_info)
str(gform_info)
```

### Multiple forms info and responses

`get_multiple_forms()` returns this kind of data.

```{r}
get_example_data("gforms_multiple")
class(gforms_multiple)
str(gforms_multiple)
```

## Slido

[You can read more about Slido data here](https://community.slido.com/analytics-and-exports-44).

`get_slido_files()` returns this kind of data.

```{r}
get_example_data("slido_data")
class(slido_data)
str(slido_data)
```

## Youtube

[You can read more about the Youtube API here](https://developers.google.com/youtube/v3).

### Channels

`get_youtube_channel_stats()` returns this kind of data.

```{r}
get_example_data("youtube_channel_stats")
class(youtube_channel_stats)
str(youtube_channel_stats)
```

### Videos

`get_youtube_video_stats()` returns this kind of data.

```{r}
get_example_data("youtube_video_stats")
class(youtube_video_stats)
str(youtube_video_stats)
```

### Session Info

```{r}
sessionInfo()
```
